Effectiveness of community-based TURF-reserves in Mexican small-scale fisheries

### 2019-08-16 docs/PLoS_manuscript.tex
Added final requests from the production team

Data for the evaluation of the SES were collected at the community-level, and focused on the Resource Systems, Resource Units, Actors, and Governance System (Table~\ref{table:ses}). Data come from official documents used in the design, creation, and implementation of the marine reserves. These include the technical studies that the cooperatives submit when they request recognition of their reserves, as well as the official enactments \cite{dof_website_2012,dof_website_2013,dof_website_2018}. We also complimented information based on the authors' experience and knowledge of the communities (RS5, RU5, A3, GS6.2, GS99.1, GS9.2, and GS10.1).

@@

IN = Isla Natividad, ME = Maria Elena, PH = Punta Herrero. Alphanumeric codes for variables follow \cite{basurto_2013-oq}; an asterisk (*) denotes variables incorporated based on \cite{difranco_2016-Xw} and \cite{edgar_2014-UO}. The presented narrative applies equally for all communities unless otherwise noted.

>>>>

Data for the evaluation of the SES were collected at the community-level, and focused on the Resource Systems, Resource Units, Actors, and Governance System (Table~\ref{table:ses}). Data come from official documents used in the design, creation, and implementation of the marine reserves. These include the technical studies that the cooperatives submit when they request recognition of their reserves, as well as the official enactments \cite{dof_website_2012,dof_website_2013,dof_website_2018}. We also complimented information based on the authors' experience and knowledge of the communities (RS5, RU5, A3, GS6.2, GS99.1, GS9.2, and GS10.1). In Table~\ref{table:ses}, the alphanumeric codes follow \cite{basurto_2013-oq}, and an asterisk denotes variables incorporated based on \cite{difranco_2016-Xw} and \cite{edgar_2014-UO}.

@@

IN = Isla Natividad, ME = Maria Elena, PH = Punta Herrero. The presented narrative applies equally for all communities unless otherwise noted. An asterisk (*) denotes variables incorporated into the framework.
